---
title: "Women's March 2017"
runtime: shiny
output: 
  html_document:
    css: marches.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


  On Saturday, January 21, 2017, women and men across the world marched for a vast array of reasons. Here is a closer look at the continental United States' participation in these marches. The orange, larger bubbles are spots with more protestors, the smaller blue ones are ares with less protestors. 



```{r echo=FALSE, warning=FALSE, message=FALSE}
library(plotly)
library(ggplot2)
library(maps)
library(dplyr)
library(tidyr)
library(RColorBrewer)
marches <- read.csv('marches.csv') 
marches <- marches %>% 
  separate(location, c("City", "State"), ", ")
marches <- marches %>% 
  filter(State != "AK") %>% 
  filter(State != "HI") %>% 
  filter(State != "Maui")
marches <- marches %>% 
  filter(Latitude > 25) %>% 
  filter(mean.high.low != "") %>% 
  filter(mean.high.low != 0)
colnames(marches)[5] <- "People"
#load us map data
all_states <- map_data("state")
#plot all states with ggplot
p <- ggplot()
p <- p + geom_polygon( data=all_states, aes(x=long, y=lat, group = group),colour="white", fill="white" )

p <- p + geom_point( data=marches, aes(label=City, x=Longitude, y=Latitude, size = People, color=People)) + 
    scale_size_continuous(range = c(2,20))
#sets scale colors
p <- p + scale_color_gradient(low='#082554', high='#f75d42')
#gets rid of lines/axis and background
p <- p + theme(panel.grid.major = element_blank(), 
               panel.grid.minor = element_blank(),
               panel.background = element_blank(), 
               axis.line = element_blank(),
               axis.title.x=element_blank(),
               axis.text.x=element_blank(),
               axis.ticks.x=element_blank(),
               axis.title.y=element_blank(),
               axis.text.y=element_blank(),
               axis.ticks.y=element_blank(),
               legend.position ="none")
ggplotly(p)

```


Although this march was not necessarily intended to be political, for many marchers, there was definitely political stimuli behind their protesting. Below is the same map as above, overlayed across a map of the 2016 election results by county.This shows locations of marches compared to the outcome of the election in the same areas.  
Light blue was a primarily Hilary county, whereas light red was a primarily Trump county. 


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)
library(ggplot2)
library(maps)
library(dplyr)
library(tidyr)
library(RColorBrewer)
marches <- read.csv('marches.csv') 
marches <- marches %>% 
  separate(location, c("City", "State"), ", ")
marches <- marches %>% 
  filter(State != "AK") %>% 
  filter(State != "HI") %>% 
  filter(State != "Maui")
marches <- marches %>% 
  filter(Latitude > 25) %>% 
  filter(mean.high.low != "") %>% 
  filter(mean.high.low != 0)
colnames(marches)[5] <- "People"
library(maps)
election <- read.csv("election.csv")
election <- election %>% 
  mutate_each(funs(tolower))
county_data <- map_data("county")
colnames(county_data)[6] <- "Place"
colnames(election)[4] <- "region"
election$Clinton <- as.numeric(election$Clinton)
election$Trump <- as.numeric(election$Trump)
election <- left_join(election, county_data, by = c("Place" = "Place", "region" = "region"))
clinton <- election %>% 
  filter(Clinton > Trump)
trump <- election %>% 
  filter(Trump > Clinton)
p2 <- ggplot() + geom_polygon(data = clinton, mapping = aes(x = long, y = lat, group = group), fill = "#b0c5e8") + coord_fixed(1.3)
p2 <- p2 + theme(panel.grid.major = element_blank(), 
                 panel.grid.minor = element_blank(),
                 panel.background = element_blank(), 
                 axis.line = element_blank(),
                 axis.title.x=element_blank(),
                 axis.text.x=element_blank(),
                 axis.ticks.x=element_blank(),
                 axis.title.y=element_blank(),
                 axis.text.y=element_blank(),
                 axis.ticks.y=element_blank(),
                 legend.position ="none")
p2 <- p2 + geom_polygon(data = trump, mapping = aes(x = long, y = lat, group = group), fill = "#e8c2b0") + coord_fixed(1.3)
p2 <- p2 + geom_point( data=marches, aes(label=City, x=Longitude, y=Latitude, size = People, color=People), alpha=.3) + 
  scale_size_continuous(range = c(2,20))
#sets scale colors
p2 <- p2 + scale_color_gradient(low='#082554', high='#f75d42')
p2
```


Data from data.world:
  Data on [marches](https://data.world/carlvlewis/womens-marches-crowd-sizes)
Data on the [election](https://data.world/kidpixo/election-usa-2016-results)

