---
title: "Mental Illness"
output: 
  html_document: 
    css: MentalIllness.css
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I am currently a student at the University of Washington. Although I am studying Infromatics, I enjoy learning about many other things, Psychology being one of them. I just finished up taking a class on Biosychology, where we ended the quarter discussing mental illness. This is a very serious topic, that many people don't know enough about. The visualizations that follow shows data on mental illness in the United States. 

First, there is a graph of any type of mental illness in the United States. 

### Any Mental Illness


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(plotly)
library(maps)
any <- read.csv("AnyIllness.csv")
depressed <- read.csv("DepressiveEpisode.csv")
serious <- read.csv("SeriousIllness.csv")
suicide <- read.csv("SuicideThoughts.csv")
code <- read.csv("StateCode.csv")

any <- any %>% 
  filter(Map.Group == 3)

any$Small..Area.Estimate <- gsub("%","", any$Small..Area.Estimate)
# creates the map of Any Mental Illness
f <- plot_ly(type="choropleth", locations=any$State, locationmode="USA-states", z=any$Small..Area.Estimate) %>% layout(geo=list(scope="usa"))  %>% 
layout(paper_bgcolor='rgb(215, 218, 224)') 
f
```

Next is a graph of the percentage of people who has ever had a depressed episode.

### Depressed Episodes


```{r, echo=FALSE, message=FALSE, warning=FALSE}
depressed <- depressed %>% 
  filter(Map.Group == 3) %>% 
  filter(! State == "District of Columbia")

depressed <- left_join(depressed, code, by = "State")

depressed$Small..Area.Estimate <- gsub("%","", depressed$Small..Area.Estimate)
# creates the map of Any Mental Illness
f <- plot_ly(type="choropleth", locations=depressed$Code, locationmode="USA-states", z=depressed$Small..Area.Estimate) %>% layout(geo=list(scope="usa")) %>% 
layout(paper_bgcolor='rgb(215, 218, 224)') 
f


```

The next graph shows any prevalence of a serious mental illness.

### Serious Mental Illness


```{r, echo=FALSE, message=FALSE, warning=FALSE}
serious <- serious %>% 
  filter(Map.Group == 3) %>% 
  filter(! State == "District of Columbia")

serious <- left_join(serious, code, by = "State")

serious$Small..Area.Estimate <- gsub("%","", serious$Small..Area.Estimate)
# creates the map of Any Mental Illness
f <- plot_ly(type="choropleth", locations=serious$Code, locationmode="USA-states", z=serious$Small..Area.Estimate) %>% layout(geo=list(scope="usa")) %>% 
layout(paper_bgcolor='rgb(215, 218, 224)') 
f
```

And finally, this shows the rates of serious thoughts of suicide in all of the states.

### Thoughts of Suicide

```{r, echo=FALSE, message=FALSE, warning=FALSE}
suicide <- suicide %>% 
  filter(Map.Group == 3) %>% 
  filter(! State == "District of Columbia")

suicide <- left_join(suicide, code, by = "State")

suicide$Small..Area.Estimate <- gsub("%","", suicide$Small..Area.Estimate)
# creates the map of Any Mental Illness
f <- plot_ly(type="choropleth", locations=suicide$Code, locationmode="USA-states", z=suicide$Small..Area.Estimate) %>% layout(geo=list(scope="usa")) %>% 
layout(paper_bgcolor='rgb(215, 218, 224)') 
f
```

Mental illness is a very serious issue, often left undiscussed in the US. If you or someone you know might be struggling with mental illness, reach out. Here are some options: [BetterHelp](https://www.betterhelp.com/), [CrisisLine](https://crisisclinic.org/find-help/crisis-line/), and [MentalHealth.gov](https://www.mentalhealth.gov/get-help/immediate-help/).

Data from [here](https://data.world/samhsa).
