---
title: "Hackers"
output: 
  html_document:
    css: hackers.css
---

The following graphs depict a list of IP addresses of people around the world that attempt (and fail) to hack the server that this website is running on. It maps a trail from our location in Seattle, WA the location at which the IP address is coming from. You can zoom in and scroll over the different locations at the end of the lines to see more information.


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(maps)
library(ggplot2)
library(dplyr)
library(plotly)
data <- read.csv("ipLatLon")
data$Latitude <- as.numeric(data$Latitude)
data$Longitude <- as.numeric(data$Longitude)

map <- map_data('world')
data2 <- data %>% 
  group_by(City, Country, Longitude, Latitude) %>% 
  summarise(Num = n())
map <- map_data('world')
p <- ggplot() + geom_polygon(data = map, mapping = aes(x = long, y = lat, group = group), fill = "#558c84") + coord_fixed(1.3) + ggtitle("")
p <- p + geom_point(data = data2, mapping = aes(x = Longitude, y = Latitude, size = Num, title = Country), color = "#8c5b55")
p <- p + geom_segment(data = data2, mapping = aes(x = -122.3321, y = 47.6062, xend = Longitude, yend = Latitude), color = "#4f4f4f", alpha=.3)
p <- p + theme(panel.grid.major = element_blank(), 
               panel.grid.minor = element_blank(),
               panel.background = element_rect(fill = "#fcecea"),
               plot.background = element_rect(fill = "#fcecea"), 
               axis.line = element_blank(),
               axis.title.x=element_blank(),
               axis.text.x=element_blank(),
               axis.ticks.x=element_blank(),
               axis.title.y=element_blank(),
               axis.text.y=element_blank(),
               axis.ticks.y=element_blank(),
               legend.position ="none")
ggplotly(p)

```

I found it interesting that many of the ip addresses came from the same location. Below is a graph showing where there were the heaviest concentrations of 'hackers' are located by country. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
data3 <- data %>% 
  group_by(Country) %>% 
  summarise(Num = n())
data3Clean <- data3 %>% 
  filter(Num > 20)
p2 <- ggplot(data3Clean, aes(x = Country, y = Num)) + geom_bar(stat="identity")
p2 <- p2 + theme(panel.grid.major = element_blank(), 
               panel.grid.minor = element_blank(),
               panel.background = element_rect(fill = "#fcecea"),
               plot.background = element_rect(fill = "#fcecea"),  
               axis.line = element_blank(),
               axis.title.x=element_blank(),
               axis.text.x=element_blank(),
               axis.ticks.x=element_blank(),
               axis.title.y=element_blank(),
               axis.text.y=element_blank(),
               axis.ticks.y=element_blank(),
               legend.position ="none")
ggplotly(p2)
```


Latitude and longitude from [here](https://freegeoip.net/?q=2601:602:9600:65ab:b97a:821:ac74:30d).
Python code that transfers the ip addresses and location into a csv; [here](https://github.com/Alimcg2/datavis/blob/master/Hackers/getLocation.py). 
